\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


\newcommand{\resumeItem}[2]{
\item\small{
  \textbf{#1}{: #2 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\href{https://linkedin.com/in/yourprofile/}{\Large Your Full Name}} & Email : \href{mailto:your.email@example.com}{your.email@example.com}\\
\href{https://linkedin.com/in/yourprofile/}{linkedin.com/in/yourprofile} & Mobile : +1-XXX-XXX-XXXX \\
\end{tabular*}

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {University Name}{City, State/Country}
    {Degree in Major;  GPA: X.XX}{Month Year -- Month Year}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Company Name}{City, State/Country}
    {Job Title}{Month Year - Present/Month Year}
    \resumeItemListStart
      \resumeItem{Project/Feature Name}
        {Brief description of your contribution, technologies used, and impact. Focus on achievements and metrics when possible.}
      \resumeItem{Another Project}
        {Description highlighting your role, technical skills, and business value delivered.}
      \resumeItem{Tech Stack}
        {List relevant technologies: e.g., Python, JavaScript, AWS, Docker, etc.}
    \resumeItemListEnd

  \resumeSubheading
    {Previous Company Name}{City, State/Country}
    {Previous Job Title}{Month Year - Month Year}
    \resumeItemListStart
      \resumeItem{Key Project}
        {Describe your responsibilities, technical approach, and measurable outcomes.}
      \resumeItem{Another Achievement}
        {Focus on problems solved, technologies learned, and team collaboration.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\resumeSubHeadingListStart
  \item{
    \textbf{Proficient}{: List technologies you use regularly and confidently (e.g., Python, Java, React, SQL)}
  }
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
  \resumeSubItem{\href{https://your_project_link.com/}{Project Name (Month Year – Month Year)}}
    {Brief description of the project, your role, technologies used, and key achievements or learnings. Include metrics if applicable (e.g., user count, performance improvements).}
  \resumeSubItem{\href{https://your_project_link.com/}{Project Name (Month Year – Month Year)}}
    {Description focusing on technical challenges overcome, features implemented, and tools/technologies utilized.}
\resumeSubHeadingListEnd

\section{Achievements and Certifications}
\resumeSubHeadingListStart
  \resumeSubItem{Award/Recognition Name}
    {Description of the achievement, competition, or recognition. Include context and significance.}
  \resumeSubItem{Certification or Honor}
    {Details about professional certifications, academic honors, or competitive achievements.}
  \resumeSubItem{Leadership Role}
    {Description of leadership positions, volunteer work, or community involvement.}
\resumeSubHeadingListEnd

\section{Languages}
\resumeSubHeadingListStart
  \item{
    \textbf{Native/Fluent}{: Language 1, Language 2}
  }
  \item{
    \textbf{Professional Working Proficiency}{: Language 3}
  }
  \item{
    \textbf{Basic/Elementary}{: Language 4}
  }
\resumeSubHeadingListEnd

\end{document}